\section{Base Classes}

While most common folk have shared ale with a fighter or perhaps even
seen a wizard perform an awesome act of magic, these are not the only
adventurers known to legends and history. The following character
classes present new options for players and greater variety for a Game
Master's cast of nonplayer characters.

\section{Base Classes}

The six new base classes presented in this book are equivalent in power
to the 11 core classes in the \emph{Pathfinder RPG Core Rulebook}. Game
Masters (also called GMs) are encouraged to allow players to choose
freely from these classes and the other additional rules and options in
this book, but each GM must make a personal decision about what is and
isn't allowed in his campaign, and the relative prevalence of such
character classes in his or her world.

Each new class presents interesting character themes and special
abilities as follows.

\textbf{\href{baseClasses/alchemist.html}{Alchemist}}: The alchemist is
the master of alchemy, using extracts to grant him great power, mutagens
to enhance his form, and bombs to destroy his enemies.

\textbf{\href{baseClasses/cavalier.html}{Cavalier}}: Mounted upon his
mighty steed, the cavalier is a brave warrior, using his wit, charm, and
strength at arms to rally his companions and achieve his goals.

\textbf{\href{baseClasses/inquisitor.html}{Inquisitor}}: Scourge of the
unfaithful and hunter of horrors, the inquisitor roots out the enemies
of her faith with grim conviction and an array of divine blessings.

\textbf{\href{baseClasses/oracle.html}{Oracle}}: Drawing upon divine
mysteries, the oracle channels divine power through her body and soul,
but at a terrible price.

\textbf{\href{baseClasses/summoner.html}{Summoner}}: Bonded to a
mysterious creature called an eidolon, the summoner focuses his power on
strengthing that connection and enhancing his strange, otherworldy
companion.

\textbf{\href{baseClasses/witch.html}{Witch}}: Lurking on the fringe of
civilization, the witch makes a powerful connection with a patron that
grants her strange and mysterious powers through a special familiar.

\section{Starting Wealth}

The following table lists the starting gold piece values by class. In
addition, each character begins play with an outfit worth 10 gp or less.

\ctable[caption = {Class Starting Wealth Average},
pos = H, center, botcap]{lll}
{% notes
}
{% rows
\FL
Class & Starting Wealth & Average
\ML
Alchemist & 3d6 × 10 gp & 105 gp
\\\noalign{\medskip}
Cavalier & 5d6 × 10 gp & 175 gp
\\\noalign{\medskip}
Inquisitor & 4d6 × 10 gp & 140 gp
\\\noalign{\medskip}
Oracle & 3d6 × 10 gp & 105 gp
\\\noalign{\medskip}
Summoner & 2d6 × 10 gp & 70 gp
\\\noalign{\medskip}
Witch & 3d6 × 10 gp & 105 gp
\LL
}
